\TheTitle

### 2017-07-13 paper/study.tex
Study procedure: adding recording method
Fixing conceptual questions results section
Fixing the wording in the conceptual questions. More concise, and more
details.

Should probably include some of the drawing from the study though.

We use a script written in python 3.6.1 in order to assure that we do no
bias the randomization, and ensure that correct ordering is maintained
between tools, tasks, and commits. The script produces the entire script
for the study, so we only need to read it to correctly conduct the
study. Re-running the script generates the study for the next
participant.

@@

@@

\dmg{this is still methodology.}
% TODO: Move to methodology
% We recorded the audio and screen capture video for each participant in
% the study for further analysis.
% \dmg{you don't need this sentence, it is redundant}
% After capturing the information, we
% extracted various metrics from the videos.
% \dmg{ you don't record, you measure}
% From the conceptual tasks, we
% recorded the time in seconds, and the answer for the question. We
% extracted three metrics for the summarization tasks, the time in
% seconds, the correctness, and the accuracy.

In task T4, the merges are important, and the order of those
merges is important to the answer. For this task, we use the edit
distance, which will increment if adding merges, removing merges, and
changing the order of the merges is necessary. T5 only asks for the set
of commits, so the order is not important, but the distance will
increase if adding or removing commits is necessary for getting the
correct answer. In T6 and T8 the answer is a single number, so the
distance is simply the difference between the answer provided and the
correct answer. In T7, there is only a single answer that is correct, so
the correctness metric and accuracy are the same, for this reason we do
not measure the accuracy of this task. The answer for T9 is similar in
requirements to T5, only asking for the set of files that had the most
changes. We use the same distance function in T9 and T10 as we did in
T5, measuring the number of items that must be added and removed from
the answer in order to change the response into the correct answer. % TODO: reword
T9 appears to be similar to T7 in that there is only a single file name
that must be provided, but in \comA, two files are modified the same
amount and are both the correct answer. In order to provide the correct
answer, the participant must be able to identify both files. In all
means of accuracy measurement, a correct answer will have a distance of
zero, while a non-zero distance indicates an incorrect answer.

@@

\dmg{i don't like the expression: we are able to see... too long.. be to the point: Table X shows/depicts/ etc ... they
  are not overviews, they are a summary}
In Table~\ref{tab:conceptual_results}, we are able to see an overview of
the results from the conceptual questions.

\begin{table*}[htpb]
  \centering
  \caption{Results from the conceptual questions\dmg{what are the columns? they need captions}}
  \label{tab:conceptual_results}
  \begin{tabular}{ll|r|lrr|rrr}
    Question                      & Commit & Answer & Median & Mean  & Variance & Median(s) & Mean(s) & Variance(s)\\\hline\hline
    Number of commits in the tree & \comA  & 1      & 4      & 19.11 & 753.11   & 10.0      & 49.92   & 5952.08\\
    Number of merges in the tree  & \comA  & 1      & 5      & 8.27  & 53.62    & 7.5       & 24.67   & 884.42\\\hline
    Number of commits in the tree & \comB  & 5      & 4      & 7.80  & 136.84   & 31.5      & 106.83  & 54123.42\\
    Number of merges in the tree  & \comB  & 3      & 3.5    & 5.40  & 50.27    & 11.0      & 65.6    & 29798.82\\
  \end{tabular}
\end{table*}

@@

It should be noted that these questions were answered after spending
roughly ten minutes attesting to draw a picture that held the answers to
these questions.

>>>>

We use a script written in python 3.6.1 in order to assure that we do no
bias the randomization, and ensure that correct ordering is maintained
between tools, tasks, and commits. The script produces the entire script
for the study, so we only need to read it to correctly conduct the
study. Re-running the script generates the study for the next
participant. We use screen capture to record the audio and video. From
the screen capture, we measure the time, as well as recording the
responses in the study.

@@

% TODO: maybe move the time measuring procedure from summ. to here

@@

\evan{This looks weird not having text between the subsections... Should
  I put something here?...}

@@

Table~\ref{tab:conceptual_results} shows a summary of the results from
conceptual tasks T2 and T3. The answer column contains the correct
answer to the corresponding task, while the median, mean, and variance
columns are with respect to the answers provided by the
participants.\evan{Is this better for describing the columns in the
  table?} The median(s), mean(s), and variance(s) columns are with
respect to the time taken, in seconds, by the participants to respond to
the tasks.

\evan{Should I add some of the drawings to the paper?}
The results from T1 did not vary greatly between the participants. The
drawings generally show something in the form of a list, starting from
the provided commit and traversing the master branch, indicating that
the participants were unable to determine which merge was in the master
branch. Many of the participants identified the next tag, v2.6.29-rc6,
to be ``the master branch'', however, a tag is not a branch. One
participant was able to draw the correct diagram for \comA directly
using the git command line, but rejected their response after inspecting
the DAG visualization provided by Gitk and proceeded to draw a list of
merges.

\begin{table*}[htpb]
  \centering
  \caption{Results from the conceptual questions}
  \label{tab:conceptual_results}
  \begin{tabular}{ll|r|lrr|rrr}
    Question & Commit & Answer & Median & Mean  & Variance & Median(s) & Mean(s) & Variance(s)\\\hline\hline
    T2       & \comA  & 1      & 4      & 19.11 & 753.11   & 10.0      & 49.92   & 5952.08\\
    T3       & \comA  & 1      & 5      & 8.27  & 53.62    & 7.5       & 24.67   & 884.42\\\hline
    T2       & \comB  & 5      & 4      & 7.80  & 136.84   & 31.5      & 106.83  & 54123.42\\
    T3       & \comB  & 3      & 3.5    & 5.40  & 50.27    & 11.0      & 65.6    & 29798.82\\
  \end{tabular}
\end{table*}

@@

It should be noted that these questions were answered after spending
roughly ten minutes attempting to draw a picture that held the answers
to these questions, so the times indicate how quickly the participant
was able to interpret their conceptual understanding.
